\phantomsection
\chaptermark{ACKNOWLEDGEMENTS}
\centerline{\normalsize\textbf{ACKNOWLEDGEMENTS}}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}
\vspace{0cm}
%\bigskip  \bigskip \bigskip \bigskip \bigskip \bigskip
%\hfill  \hfill \hfill
\smallskip

I would like to thank the Almighty for giving me the strength, knowledge, ability, and opportunity to undertake this research study and to persevere and complete it satisfactorily.

First and foremost, I would like to express my deep sense of profound gratitude to my research supervisor \textbf {Dr. M. P. Selvan}, \textit{Associate Professor/EEE}, \textit{NIT Trichy} for his constant guidance, support, and motivation during my research work. His systematic and planned approach had consistently motivated me towards all activities including the completion of the research work in time. His valuable suggestions and comments at appropriate times during this investigation have contributed a lot in smooth conduct of the research work. Motivation, appreciation, moral support, and flexibility permitted during the course have helped me to complete my research successfully.

Besides my research supervisor, I would like to thank the rest of my General Test Committee members: \textbf{Dr. N. Kumaresan}, \textit{Professor/EEE}, \textit{NIT Trichy}, \textbf{Dr. S. Moorthi}, \textit{Associate Professor/EEE}, \textit{NIT Trichy}, and \textbf{Dr. K. Ranjith Kumar},\textit{ Associate Professor/EEE}, \textit{GCT Coimbatore} for their insightful comments and encouragement, which have led me to widen my research from various perspectives.

My sincere thanks to \textbf{Dr. P. Raja} and \textbf{Dr. M. Venkata Kirthiga}, \textit{Associate Professors} of \textit{EEE Department}, \textit{NIT Trichy} for extending their support during the course of this research work.

I would like to thank the \textbf{Ministry of Human Resource Development (MHRD)}, \textit{Government of India}, for granting the financial support during the M.S.(By Research) program. I would also like to thank the Director: \textbf{Dr. Mini Shaji Thomas}, Deans (Academic): \textbf{Dr. C. Nagamani} and \textbf{Dr. S. Shanmugam}, and Associate Deans (M.S./Ph.D.): \textbf{Dr. R. Karvembu} and \textbf{Dr. P. Muthuchidambaranathan}  of  \textit{NIT Trichy} for providing their extended support towards smooth conduct of the research work at the institute. 

I would like to express my sincere gratitude to the \textbf{Ministry of Electronics and Information Technology}, \textit{Government of India} for providing financial support under Visvesvaraya Young Faculty Research Fellowship during this research work.

I must also thank the HoDs: \textbf{Dr. K. Sundareswaran} and \textbf{Dr. S. Sudha}, faculty members, and staffs of the \textit{Department of Electrical and Electronics Engineering}, \textit{NIT Trichy} for their kind help and support.

I would also like to thank \textbf{Dr. S. Muthukumaran}, \textit{Associate Professor/MME} and \textit{Head (Intellectual Property Right Cell)}, NIT Trichy for his extended support.

I would also like to thank \textbf{Dr. A. K. Bakthavatsalam}, \textbf{Mr. R. Gururaj}, and the student placement representatives of \textit{Department of Training and Placement}, \textit{NIT Trichy} for their kind help and support.

I must acknowledge the extended support of my fellow M.S. scholars and friends: \textbf{Mr. S.V. Hareesh, Mr. Rufzal, Mr. Abhishek A., Mr. Abhilash M., Mr. Yashwant, Mr. Kartikeya, Mr. Pawan, Mr. Puneet, Mr. Dibyaraj}, and \textbf{Mr. Ritesh Acharya.}

I must acknowledge the extended support of my fellow Ph.D. scholars and friends: \textbf{Dr. Arun S.L., Dr. Suman M., Dr. A. Dheepan C., Dr. R. Vijaya Priya, Mrs. S. Aditya, Mrs. Suhanya P., Ms. Jenisha Charles, Mr. B. Hanumantha Rao, Mr. Nageshwara Reddy, Mr. J. Ganesh Moorthy, Mr. C. Subbanna, Mr. M.S.R. Niranjan, Mr. P. Ponraj, Mr. N. Shekhar}, and \textbf{Mohammed Mansoor}.

I must acknowledge the extended support of my fellow M.Tech. friends: \textbf{Mr. Aryesh Namboodiri, Mr. Gopinath V., Mr. Alok Dwivedi, Mr. Vaibhav Chauhan, Mr. Manish, Mr. Junaid, Mr. Soven, Mr. Sumit, Mr. Vinod, Mr. Santosh, Mr. Aditya Gedda, Mr. Khetal, Mr. Amit Roy}, M.Tech./PEPS (2018 Batch) and all other M.Tech. students associated with HES Lab.   

I must acknowledge the extended support of my fellow B.Tech. friends: \textbf{Mr. Dinesh, Mr. Sudharsan, Mr. Joshua, Mr. Kumar Teja, Mr. Subhadeep, Mr. Paveen, Mr. Aditya K. Mishra, Mr. Laxman, Mr. Shakeel, Mr. Ganesh R., Mr. Vijay, Mr. Veejay, Mr. Amar, Mr. Shantanu, Mr. Pramod, Mr. Preetham, Mr. Nitin, Mr. Mohit, Mr. Satyam, Mr. Ashutosh}, B.Tech./EEE (2019 Batch), and all other B.Tech. students associated with HES Lab.

I must acknowledge the extended support of my B.Tech. batchmates: \textbf{Mr. Sunil, Mr. Vikas, Mr. Radhakrishna, Mr. Sunischit, Mr. Tarun, Mr. Shubham}, and \textbf{Mr. Saurabh}.

I owe my utmost gratitude to my parents \textbf{Shri Ranjit Kumar Singh} and \textbf{Smt. Rajni Singh} for their love and support throughout my life. I thank both for giving me strength, guidance, and freedom to chase my dreams. I must thank my brother \textbf{Mr. Priyesh Singh} for being a constant pillar of support. I would also like to thank my late paternal grandparents: \textbf{Shri Mahesh Narayan} and \textbf{Smt. Shakuntala Devi}, and my maternal grandparents: \textbf{Shri R. R. Rawani} and \textbf{Late Smt. Janaki Devi} for their prayers to achieve this glorious mark. I am grateful to my uncles, aunts, brothers, sisters, brothers in law, niece, nephew, cousins and all my relatives for their wishes and support. Finally, I cannot forget thanking the mother \textbf{Nature} for providing everything.

There are few more uncredited good hearts behind this success. I would like to thank every one of them.

Again, I am very grateful to my supervisor and my family, who believed and encouraged me for making this mission possible.

\vspace{0.25in}
\begin{flushright}
\textbf{SHASHANK SINGH}
\end{flushright}

\newpage