\phantomsection
\chaptermark{LIST OF PAPERS BASED ON THE THESIS}
\newpage
\centerline{\normalsize\textbf{LIST OF PAPERS BASED ON THE THESIS}}%\\
\addcontentsline{toc}{chapter}{LIST OF PAPERS BASED ON THE THESIS}
\vspace{0cm}
\smallskip
\subsubsection*{Patent Filed}
\begin{enumerate}
\item \textbf{Singh, S.}, \textbf{A. Roy} and \textbf{M.~P. Selvan} Smart Load Node System for Operating an Appliance and Method Thereof. \textit{Intellectual Property India Journal}, March 01, 2019, App No. 201741039083 dated November 2, 2017.    
\end{enumerate}
\subsubsection*{Refereed Journals}
\begin{enumerate}
\item \textbf{Singh, S.}, \textbf{A. Roy} and \textbf{M.~P. Selvan} (2019) Smart load node for nonsmart load under smart grid paradigm: a new home energy management system. \textit{IEEE Consumer Electronics Magazine}, \textbf{8}(2), 22--27.
\end{enumerate}
\subsubsection*{International Conferences}
\begin{enumerate}
\item \textbf{Singh, S.}, \textbf{A. Namboodiri} and \textbf{M.~P. Selvan} (2019) Simplified algorithm for dynamic demand response in smart homes under smart grid environment. \textit{IEEE PES GTD Grand International Conference \& Exposition Asia}, Bangkok, Thailand.
\item \textbf{Singh, S.} and  \textbf{M.~P. Selvan} (2019) A smart energy meter enabling self-–demand response of consumers in smart cities of Tamil Nadu. \textit{International Conference on Smart Cities Model (ICSCM 2019)}, IIT Madras, Chennai, India.
\item  \textbf{Dinesh, P.}, \textbf{K.~K.~Teja}, \textbf{S. Singh}, \textbf{M.~P. Selvan} and \textbf{S. Moorthi} (2018) FPGA Based SoC Estimator and Constant Current Charging/Discharging Controller for Lead--Acid Battery. \textit{IEEE India Council Conference (INDICON)}, Coimbatore, India.
\item \textbf{Singh, S.}, \textbf{Arun S.~L.} and \textbf{M.~P. Selvan} (2017) Regression based approach for measurement of current in single--phase smart energy meter. \textit{2017 IEEE Region 10 Symposium (TENSYMP)}, Cochin, India.
\end{enumerate}
\subsubsection*{Papers Under Review}
\begin{enumerate}
\item \textbf{Singh, S.}, \textbf{S. Thirumalai} and \textbf{M.~P. Selvan} Realization of self-demand response through non-intrusive load monitoring algorithm. \textit{IEEE CONECCT 2019}, IIIT Bangalore.
\end{enumerate}